
\chapter{The Framework (15-20 pages)}

\section{DES Theoretical Framework}

\subsection{Notation}

The notation used in this document is the one in
\cite{cassandras_introduction_2010}. For the benefit of the reader we place here
the most essential notation necessary for understanding of the further material.

Let $\Sigma$ be a finite set of events. A sequence of events is a string.
$\Sigma^*$ denotes a set of all finite strings over $\Sigma$.
$L\subseteq\Sigma^*$ is a language over $\Sigma$. Given strings $s$ and $t$,
$st$ is their concatenation. Given strings $s$ and $w$, $w$ is a prefix of $s$
if exists $t$ such that $wt = s$. Prefix closure of $L$, denoted by
$\overline{L}$ is a set of all prefixes of all the strings in $L$.
If $\overline{L} = L$ then $L$ is prefix-closed. The post language of $L$ after
a string $s$ is denoted as $L/s$, i.e. $L/s := \{t\mid st \in L\}$. We
write $\sigma \in s$ if the event $\sigma \in \Sigma$ appears in the string $s
\in \Sigma^*$. If $\{s\}$ is a singleton, we write $s$ for operations on
languages.

An automaton $G$ is a tuple $$G := \left< X,\Sigma,\delta,x_0, X_m \right>,$$
where $X$ is a set of states, $x_0 \in X$ is an initial state, $X_m \subseteq X$
is the set of marked states, and $\delta: X \times \Sigma \rightarrow X$ is the
transition function.
We say a language $L := \mathcal{L}(G)$ is generated or recognized by the
automaton $G$. In this paper we assume that for each language there is always a
correspondent automaton, and vice versa. The marked language $L_m \subseteq L$
is intended to make a part of the automaton's behaviour distinguishable in a
certain context.

Some events of DES can not be observed. To reflect that the set of events
$\Sigma$ is partitioned into disjointed sets of observable events $\Sigma_o$ and
not observable events $\Sigma_{ou}$, i.e. $\Sigma = \Sigma_o~\dot{\cup}~
\Sigma_{ou}$.
$M: \Sigma^* \rightarrow \Sigma_o^*$ denotes natural projection that
erases unobservable events.
% ; $\epsilon$ means the empty string. 
The correspondent inverse projection is $M^{-1}: \Sigma_o^* \rightarrow
2^{\Sigma^*}$.

Let $I := \{1,2,\ldots,n\} \subset  \mathbb{N}$ be an index set. A system is
defined by a set of automata $\{G_{i \in I}\}$ and a correspondent set of
languages $\{L_{i \in I}\}$. We use the term \emph{local} in context of the
automata and languages from these sets. The \emph{global} language of the system
is defined by the parallel composition \cite{cassandras_introduction_2010} of
its local languages:
$L := \parallel_{i \in I} L_i$.
The natural projection for the local languages is defined as 
$P_i := \Sigma^* \rightarrow \Sigma_i^*$. We extend it to the system's languages
as follows: $P_i(L) := \{s\mid s\in L_{i}\}$, and 
$P_i^{-1}(L_{i}) := \{s \mid s \in L, P_i(s) \in L_i\}, ~i \in I$.
We also define natural projection over observable events for the index set: 
$M_i :\Sigma_i^* \rightarrow \Sigma_{i,o}^*$, natural projection over common
events:
$P_{i,c} : \Sigma_i^* \rightarrow (\Sigma_i \cap \bigcup_{j\neq
i}^I\Sigma_j)^*$, and natural projection over observable and common events:
$P_{i,co} : (\Sigma_i \cup \Sigma_o)^* \rightarrow (\Sigma_{o} \cup (\Sigma_i
\cap \bigcup_{j\neq i}^I\Sigma_j))^*$. All the above projections, as well as
the correspondent inverse projections, are defined also for languages in the
usual manner.


\subsection{Abstraction}
For model checking and verification the state explosion problem is one of
the main limitations for their application in industry. The most important
technique to deal with the state explosion problem is abstraction. The basic
idea of abstraction is that parts of a system \emph{does not have effect} on the
particular properties. These parts can be \emph{eliminated} from the design.

One of the most effective abstraction techniques, compositional reasoning,
deals with complex systems in order to reduce its complexity by breaking into
smaller parts, checking its properties and then deducing the system correctness. These parts
does not necessary reflect the real structure of a system if any. On the other
hand the most of the systems are already structured in reality. Their structure
is understood by humans, the properties of their parts can be described and
checked easier relatively to the complex system. Then the models of the part
along of their properties can be reused.

When a system is built from its components, the state explosion problem rises
on the parallel (synchronous) composition of component's models. Then it seems
rational to modify the description of a complex system such that a parallel
composition of component's models can be avoided, and tune the analysis
techniques to suit the new description.

\section{Modeling Framework (Matteo's work)}


\section{Diagnosability in DES \ldots}

In Discrete-Event Systems, diagnosis of a fault is a problem of deciding whether
or not the fault occurred, under partial observation of the system's events.
The problem was defined in \cite{sampath_diagnosability_1995} where the authors
consider a monolithic model of a system. This definition and new definitions
of diagnosability problem, emerged later, may be grouped as, for example, in
\cite{su_global_2005}, where an approach can be centralized as in
\cite{sampath_diagnosability_1995}, \cite{jiang_polynomial_2001} and
\cite{yoo_polynomial-time_2002}, 
decentralized as in \cite{debouk_coordinated_1998},
\cite{pencole_formal_2005} and \cite{qiu_decentralized_2006}, 
or distributed as in \cite{su_distributed_2002}.
The centralized and decentralized approaches require building of a monolithic
model. This process corresponds with exponential growth of the model's state
space, which makes the diagnosability problem intractable for complex large
systems with high modularity.

Architectures for on-line diagnosis can be categorized as follows:
centralized, decentralized and distributed.


\begin{figure}[!ht]
\centering
\begin{tikzpicture}
	\node[draw]		(0)	at (1, 3) 		{$L_1$};
  \node[] (fake) [above of=0]              {}; %for space above the picture
	\node[]			(1)	[right of = 0]	{$\ldots$};
	\node[draw]		(2)	[right of = 1]	{$L_n$};
	\draw[dashed] (0, 2.5) rectangle (4, 3.5);
	\node[]			(3) at (2, 2.6) {};
	\node[draw]		(4) at (2, 1) {$D$};
	\draw[->] (3) -- (4);
	\node[]	at (3, 1.8) {$M(\parallel_{i} L_i)$};
	\node[]		(5) [below of = 4] {};
	\draw[->] (4) -- (5);
	\draw[] (0, -.5) rectangle (4, 0.1);
	\node[]			(3) at (2, -.2) {Decision};
\end{tikzpicture}
\caption{Architecture of a system with centralized diagnosis}
\label{fig_centralized}
% \end{figure}
% 
% \begin{figure}[t]
% \centering
\begin{tikzpicture}
	\node[draw]		(0)	at (1, 3) 		{$L_1$};
   \node[] (fake) [above of=0]              {}; %for space above the picture
	\node[]		(0)	at (1, 3) 		{$L_1$};
	\node[]			(1)	[right of = 0]	{$\ldots$};
	\node[draw]		(2)	[right of = 1]	{$L_n$};
	\draw[dashed] (0, 2.5) rectangle (4, 3.5);

	\node[]			(000)	at (1, 2.6) {};
	\node[draw]		(00) [below of = 000] {$D_1$};
	\node[]			(10) [below of = 00] {$$};
	\draw[->] (000) -- (00);
	\draw[->] (00) -- (10);

	\node[]			(1)	[right of = 0]	{$\ldots$};
	\node[]			(11)[right of = 00]	{$\ldots$};

	\node[]			(222)	at (3, 2.6) {};
	\node[draw]		(22) [below of = 222] {$D_n$};
	\node[]			(20) [below of = 22] {$$};
	\draw[->] (222) -- (22);
	\draw[->] (22) -- (20);

	\node[]	at (0, 1.5) {$M(L_1)$};
	\node[]	at (4, 1.5) {$M(L_n)$};

	\draw[] (0, 0.7) rectangle (4, 0.1);
	\node[]			(3) at (2, .4) {Decision};
\end{tikzpicture}
\caption{Architecture of a system with decentralized diagnosis}
\label{fig_decentralized}
\end{figure}

\begin{figure}[t]
\centering
\begin{tikzpicture}
	\node[draw]		(0)	at (1, 2) 		{$L_1$};
  \node[] (fake) [above of=0]              {}; %for space above the picture
	\node[draw]		(00) [below of = 0] {$D_1$};
% 	\node[draw]		(p0) [below of = 00] {Decision$_1$};
	\node[]			(10) [below of = 00] {};
	\draw[->] (0) -- (00);
	\draw[->] (00) -- (10);

	\node[]			(1)	at (3, 2)	{$\ldots$};
	\node[] at (3, 1.3) {Communication};

	\node[draw]		(2)	at (5, 2) 		{$L_n$};
	\node[draw]		(22) [below of = 2] {$D_n$};

	\draw[] (.6, 0.1) rectangle (5.4, -0.5);
	\node[]			(3) at (3, -0.2) {Decision};

% 	\node[draw]		(p2) [below of = 22] {Decision$_n$};
	\node[]			(20) [below of = 22] {};
	\draw[->] (2) -- (22);
	\draw[->] (22) -- (20);
	\draw[] (00) -- (22);

	\node[]	at (0, 1.5) {$M(L_1)$};
	\node[]	at (6, 1.5) {$M(L_n)$};
\end{tikzpicture}
\caption{Architecture of a system with distributed diagnosis}
\label{fig_distributed}
\end{figure}

\subsection{Centralized diagnosability}
This architecture refers to a global model (language).If the system is modular,
then the global language is built by the parallel composition of the local
languages. All the observations are performed at one site. In this architecture
only one diagnoser $D$ \cite{sampath_diagnosability_1995} is constructed. Upon
the current state of the diagnoser a decision on the fault occurrence is made.
The structure is depicted in Figure \ref{fig_centralized}.

\subsection{Decentralized diagnosability}
This approach also exploits the entire model built from its modules, but several
local sites perform observations using only local diagnosers.
The diagnosers do not communicate to each other, but they provide necessary
information (via a protocol) to a central decision node. This architecture is
depicted in Figure \ref{fig_decentralized}.

\subsection{Distributed diagnosability}
The architecture is depicted in Figure \ref{fig_distributed}.
The distributed approach does not require to built the entire model of the
system. The architecture implies that the system has a set of observation spots,
and each spot observes only one module of the system. A communication among
observation spots is possible in order to make a decision about a fault
occurrence. 


The notion of modular diagnosability meets the same architectural implications,
and we refer to it as to the distributed approach when the amount of information
the observation spots communicate to each other is equal to zero.

Distributed approach does not require to built an entire model of the system.
The approach implies that the system has a set of observation spots, carrying
diagnosability information (diagnosers), each observing only a part of the
system (a subset of the modules, composed). Diagnosers can communicate to each
other in order to decide if a fault occurred. In general, the bigger the
observation spots for the same system, the less communications among the spots
is required.
Figure \ref{fig:curves} shows that the average size of a composed module grows
while the system's modules are composed together (we imply that each module is
represented by automata, and the size of a module is reflected by the number of
states of a correspondent automaton).
The shape of this curve depends mostly on the order the modules are taken for
the composition, but the initial point, when the system has maximal modularity,
and the final point, when all the modules are composed into one monolithic
model, remain the same. Assuming that the system is diagnosable, the average
size of a diagnoser grows much faster, since it is exponential with respect to
the average size of a module, in the worst case.
The amount of events the diagnosers have to exchange among each other, in order
to decide if a fault occurred, is decreasing. The reason the diagnosers require
less event for decision making is due to the fact that they become more
self-sufficient, since amount of observable events available for each
diagnoser without communications is growing. Thus, the events exchange rate
decreases down to the point where no communications is required to make a
decision about the faults occurrence. That is the point when the system becomes
modular diagnosable (the notion of modular diagnosability was introduced in
\cite{contant_diagnosability_2006}). The following composition of the modules
does not affect diagnosability, and leads only to the growth of the modules' and
diagnosers' sizes.

In our approach, given a system with an initial natural modularity, we search
for a point, when the system is modular diagnosable. If the system is diagnosable,
then this point can always be found. The modules correspondent to that
modularity we call \emph{virtual}, since they differ from natural modules and
used only to build diagnosers.

\begin{figure}[t]
\centering
\begin{tikzpicture}
% \draw[help lines] (0,0) grid (5,3);
% Axis 
\draw [thick, <->] 
	(0,3) node[left]{Events} -- 
	(0,0) node[below]{0} -- 
	(6,0) node[below]{1} -- 
	(6,3) node[right]{States};
\node [below] at (3,0) {1/Number of modules};
% Curve of the average size of modules
\draw[blue, thick] (0.1,.1) to [out=0,in=-170] (6,2.5); 
% Curve of the average size of diagnosers
\draw[red, thick, dashed] (0.1,.3) to [out=0,in=-140] (4,3); 
% Curve of the amount of communication
\draw[orange, thick, dotted] (0.1,2.5) to [out=-15,in=160] (3.5,0); 
% Line of the point with virtual modularity
\draw[dashed] (3.5,0) -- (3.5,3);
% Point of virtual modularity  
\draw [fill] (3.5,0) circle [radius=0.05];
\draw [fill, blue] (3.5,1.42) circle[radius=0.05] 
	node[align=left, black, below right] {Virtual\\ modules}; 
\draw [fill, red] (3.5,2.55) circle [radius=0.05];
% Legend
\draw[blue, thick] (0,-1.5) -- (1,-1.5)
	node[black, right] {Average size of module, states};
\draw[red, thick, dashed] (0,-2) -- (1,-2)
	node[black, right] {Average size of diagnoser, states};
\draw[orange, thick, dotted] (0,-2.5) -- (1,-2.5) 
	node[black, right] {Events exchange rate};

\end{tikzpicture}
\caption{Size of modules, diagnosers, and events exchange rate, changing 
with respect to the degree of modularity of the system}
\label{fig:curves}
\end{figure}



\subsection{Diagnosability of a Modular System}

Diagnosability analysis uses a notion of a faulty language to describe the
faulty behaviour of a discrete-event system. This section discuses design issues
related to representations of the faulty language and focuses on a definition
of modular diagnosability.

The faulty behavior is usually modeled by introducing fault events or by faulty
specifications. We refer to this approaches as to \emph{event-based} and
\emph{specification-based} correspondingly. All the aforementioned works exploit
the event-based approach, whereas the works \cite{zhou_decentralized_2008} and
\cite{sartini_methodology_2010} are examples of the specification-based one.

In the event-based approach fault events are a special type of event such that
$\Sigma_{uo}$ can be disjointed into the sets of faults $\Sigma_f$ and
non-faults $\Sigma_{uo}\backslash \Sigma_f$. A string containing a fault event
is called \emph{faulty string}. A set of faulty strings is called \emph{faulty
language}, i.e. formally 
$$L_f := \{ s \in L \mid \sigma \in s, \sigma \in \Sigma_f\}.$$ 
By definition, the faulty language is not necessarily prefix-closed,
$L_f \subseteq \overline{L_f}$. Thus, in the event-based approach the language
of the system can be partitioned into faulty and non-faulty languages, where the
\emph{non-faulty language} is defined as $L_{nf} := L \backslash L_f$.

In the case of the specification-based approach the faulty specification allows
us to define undesired behavior when the fault events are not necessarily
introduced. In this case this behaviour can be represented by a marked
language $L_f := L_m \subseteq L$. Labeling automata's states for the same
purpose can be considered as an equal technique.

Different types of undesired behaviours (or types of faults) are defined by
partitioning $\Sigma_f$ into subsets (not necessarily disjoint) or by several
faulty specifications for the same language. 

A faulty language defined in the event-based approach can be simply converted
into a faulty specification by marking faulty strings, and erasing fault events.
Then, we can assume that if fault events are defined, then faulty specifications
can also be defined. Consequently, a set of different types of faults requires a
correspondent set of specifications.
Thus, a method suitable for the specification-based approach implies that it can
be adopted for the event-based approach. In this paper, for the sake of
unification, we use specification-based approach. For this reason the
definitions of diagnosability originally developed by their authors for the
event-based approach are slightly modified with no loss of meaning.

For the sake of simplicity, in the following we assume that there is only one
type of fault, and that the language of the system is live.

We define \emph{diagnosability of a fault} as follows:
\begin{definition} 
\label{def:fault_is_diag}
Given a system's language $L$ with a fault defined by the sublanguage $L_f$. The
fault is diagnosable if there is no two strings in the language $L$ with the
same observation such that one string is faulty and of arbitrary cardinality,
and another is non-faulty, i.e. if the following holds:
\end{definition}
\begin{equation}
\begin{array}{l}
	\forall(s \in L_f, t \in L_f/s) 
	\\
	(\exists n \in \mathbb{N})
	(|t| \geq n) 
	\\
	\left[ M(st) \cap M(L_{nf}) = \emptyset \right].
\end{array}
\end{equation}

We define \emph{diagnosability property of a language} as follows:
\begin{definition}
The language is diagnosable if all its faults are diagnosable.
\end{definition}
The two above definitions altogether are similar to the Definition 1 in
\cite{sampath_diagnosability_1995}. We recall the statement in
\cite{contant_diagnosability_2006} proved by Theorem 2, that the global
language of the system is not diagnosable only if exists at least one non-diagnosable
local language. If all the local languages are diagnosable then the global
language is diagnosable. We refer to this property as to a local diagnosability
property:

\begin{definition}[Local diagnosability] Given the set of languages
$\{L_{i \in I}\}$. The global language $L := \parallel L_i$ is
diagnosable locally if each local language $L_i$ is diagnosable, i.e. if
the following holds:
\end{definition}
\begin{equation}
\begin{array}{l}
	\forall(i \in I, s \in L_{i,f}, t \in L_{i,f}/s)
	\\
	(\exists n \in \mathbb{N})
	(|t| \geq n)
	\\
	\left[ M_i(st) \cap M_i(L_{i,nf}) = \emptyset \right].
\end{array}
\end{equation}

The definition of modular diagnosability extends the definition of local
diagnosability as it takes into account the case when a faulty string locally
indistinguishable in one module becomes distinguishable due to the
composition with another module:

\begin{definition}[Modular diagnosability] Given the set of local languages
$\{L_{i \in I}\}$ and its correspondent sets $\{L_{i,f}\}$ and
$\{L_{i,nf}\}$. The global language $L := \parallel L_i$ is \emph{modularly
diagnosable} with respect to
$M_i: \Sigma^* \rightarrow \Sigma_{i,o}^*$ 
if the following holds:
\end{definition}
\begin{equation}
\begin{array}{l}
	\forall(i \in I, s \in L_{i,f}, t \in L_{i,f}/s)
	\\
	(\exists n \in \mathbb{N})
	(|t| \geq n)
	\\
	\left[ M_i(P_i^{-1}(st)) \cap M_i(P_i^{-1}(L_{i,nf})) = \emptyset \right].
\end{array}
\end{equation}

It was proved in \cite{contant_diagnosability_2006} by Theorem 2, Part 2 
that the local diagnosability implies the modular diagnosability\footnote{In
\cite{zhou_decentralized_2008} the authors show that the local diagnosability
and modular diagnosability are not comparable but they have a different setup
for the problem.}, i.e.
\begin{equation}
\begin{array}{l}
	\forall(i \in I, s \in L_{i,f}, t \in L_{i,f}/s)
	\\
	(\exists n \in \mathbb{N})
	(|t| \geq n)
	\\
	\left[
	\left( M_i(st) \cap M_i(L_{i,nf}) = \emptyset \right)
	\Rightarrow \right.
	\\ 
	\left.
	\left( M_i(P_i^{-1}(st)) \cap M_i(P_i^{-1}(L_{i,nf})) = \emptyset \right)
	\right].
\end{array}
\end{equation}


Recall the Definition \ref{def:fault_is_diag} of the diagnosable fault. If a
module is not diagnosable locally then exist at least two strings in its
language, one is faulty and the other one is not, with the same observation of
arbitrary length, i.e. the strings are \emph{not distinguishable}. The
indistinguishability can disappear if and only if:
$a)$ at least one string is not in its language due to concurrency with other
module, and then the strings would be distinguishable locally - the verification
of the modular diagnosability property is devoted to find if this is the case;
$b)$ indistinguishability is broken globally by interleaving sequences of the
module's events with observable events of other modules. The later case is
expressed in the following conjecture:
\begin{conjecture} Given a system of two modules with languages $L_1$ and $L_2$,
and the global language $L := L_1 \parallel L_2$. Suppose there is only
one faulty string $s \in L_1$ such that it is not distinguishable from at least one
string of $L_1\backslash s$. Thus, $L_1$ is not locally diagnosable. Suppose the
system is not modular diagnosable. Then the global language $L$ is diagnosable
only if all the strings $t \in P_1^{-1}(s)$ change their observation due to 
the composition with the language $L_2$.
\end{conjecture}

The above conjecture gives the insight into the underlining idea of our
approach. If we find a module which makes the faulty string distinguishable
then the composition of that module with a faulty one would result in a new
module satisfying the property of local diagnosability, thus improving
the modular diagnosability property of the system. In the following section we
provide a formal description of the problem.