\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}

\chapter{Main Chapter (20-30 pages)}

The setup for the problem is following. Let a system be defined as a set of
local languages $\{L_{i\in I}\}$, and let a faulty behaviour be defined for any
$i \in I$, i.e. each language $L_i$ can be disjoint into faulty and non-faulty
sublanguages: $L_{i,f}$ and $L_{i,nf}$. We assume that a faulty behaviour is
defined in a \emph{specification-based}, rather then \emph{event-based}, way.
For the sake of simplicity, we assume that a language may have only one type of
fault. We assume that $(\forall i \in I)\left[ L_i = P_i(L)\right]$. The
motivation for this assumption is following. Most of real-life complex systems
are of high modularity, where each module is presented as a small model along
with correspondent faults as, for example, in \cite{sartini_methodology_2010}.
When properly designed, such systems have neither deadlocks nor trajectories
which never executed. In practice, such assumption may require construction of a
supervisor, and verification that a local language of each module is globally
consistent, before checking diagnosability of the system.

First, we recall definition of diagnosability by virtual modules, introduced in
\cite{myadzelets_virtual_2013}.
Let $J$ be a partition of $I$. Given a set of system's languages $\{L_{i \in
I}\}$ and a set of observable projections $\{M_j \mid j \in J \}$. 
The system is modularly diagnosable with respect to $J$ and $\{M_j\}$ 
if the following holds:
\begin{equation}
	\begin{array}{l}
		\forall(i \in I, s \in L_{i,f}, t \in L_{i,f}/s)
		\\
		(\exists n \in \mathbb{N})
		(|t| \geq n)
		\\
		\left[ M_j(P_i^{-1}(st)) \cap M_j(P_i^{-1}(L_{i,nf})) = \emptyset \right].
	\end{array}
\end{equation}
The definition requires each fault originated in any language of the subset $j$
to be diagnosed by observing only events of the languages from the same subset
$j$.
% However, the languages $L_j$ are not given, and they do not have to be necessary
% constructed. That is why we use the term \emph{virtual module} as a synonym for
% the subset $j$.

Second, we recall Lemma 2 \cite{myadzelets_virtual_2013}, where the statements
hold for a system of two languages, and rewrite it for an arbitrary couple
of languages as follows.

\begin{lemma}
\label{lem:distinguished}
Given a tuple $\left< L_i, L_j, s, u\right> \mid i, j \in \mathbb{N}, i\neq j$
and $s, u \in L_i$. The strings $s, u$ are
distinguished in the language $L_i \parallel L_j$ if for the string $s$ exists
an adjacent observable support $K_j \subseteq L_j$ which satisfies the
condition:
\end{lemma} 
\begin{equation}
\label{con:distinquished}
	\begin{array}{l}
	 	(\forall t \in K_j)
	 	(\exists \sigma \in t \mid \sigma \in \Sigma_i \cap \Sigma_j)
	 	(\sigma \not \in u)
	 	\\
	 	(\forall w\sigma \in \overline{t})
	 	[M_j(t / w\sigma) \neq \emptyset].
	\end{array}
\end{equation}
% where $M'_j: (\Sigma_i \cup \Sigma_j)^* \rightarrow (\Sigma_{j,o}\backslash
% \Sigma_i)^*$.
Informally, the lemma imposes a requirement for the string $s$ to have an
\emph{observable support} (subset of observable strings ending with common
events) in another language, which guaranties that we can observe some events in that
language before any continuation of the string $s$.
Then, the lemma defines a condition which allows us to distinguish these
observations from the observation of the string $u$.

Now, we rewrite Lemma 3 \cite{myadzelets_virtual_2013}, in the context of our
setup, as follows:
\begin{lemma}
\label{lem:virtual_module_is_diagnosable}
Given a virtual module $j \in J$, the module is diagnosable with respect to
$M_j$ if:
\end{lemma}
\begin{equation}
	\begin{array}{l}
% 		(\forall i \in j, s \in L_{i,f}, t \in L_i \backslash \overline{L_{i,f}})
		(\forall i \in j, 
			s \in P_i^{-1}(L_{i,f}), 
			t \in P_i^{-1}(L_{i,nf}))
% 			t \in P_i^{-1}(L_i) \backslash \overline{P_i^{-1}(L_{i,f})})
		\\
		(\exists k \in j \mid k \neq i) \textrm{ and }
		\\
		\textrm{condition (\ref{con:distinquished}) holds for at least one of
		the tuples:}
		\\
		\left<P_i^{-1}(L_i), L_k, s, t \right>,
		\left<P_i^{-1}(L_i), L_k, t, s \right>.
	\end{array}
\end{equation}
The lemma implies, that the virtual module is diagnosable if we can distinguish
all faulty strings from all non-faulty strings. 
% excluding all prefixies of the faulty strings
% Note, that exclusion of the prefixes comes from fact that the non-compositional
% analysis is used.
From the lemma it can be seen that for one faulty sublanguage there can be a
subset of languages with observable supports (a few $k\in j$), satisfying the
conditions.
In order to make the system modularly diagnosable, thus, one needs to find a
relevant partition, with a desired distribution of modules over the partition.
It worth to note, that the partitioning implies that languages with faults are
in subsets with the languages which have observable events. Thus, other
languages which have no faults and have no observable events, as well the
languages with observations which have no effect for the diagnosability
property, will be in other subsets.

One faulty module may require a few modules with observable supports.
The algorithms presented in the following section are aimed to find such subset
of system's modules. The first algorithm may be viewed as a \emph{forward
propagation} procedure. It starts from the faulty module, and propagates faulty
and non-faulty information trough all the modules, according to some
of requirements of the lemmas \ref{lem:distinguished} and
\ref{lem:virtual_module_is_diagnosable} related to common events. The second
algorithm may be viewed as a \emph{backward propagation} procedure. It starts
from a module with observable support, and propagates information related to
observable events toward the faulty module, according to the rest of the lemmas'
requirements.


\section{Algorithms for diagnosability by virtual modules}
\label{sec:algorithms}

Assume that a language with a faulty behaviour and a language which has an
observable support are given. Then, it's required to verify if the observable
support is either for the faulty or non-faulty sublanguages. If it is true, then the
correspondent modules can be composed into a virtual module.
According to the Lemma \ref{lem:virtual_module_is_diagnosable}, in order to
decide if the virtual module is diagnosable we need to verify the necessary
conditions for all the strings $P_i^{-1}(L_{i,f})$ and $P_i^{-1}(L_{i,nf})$,
projected to the local languages of other modules $\{j \in I\mid j \neq i\}$.
Those local projections are the basic elements our algorithms operate with. In the sequel we
refer to the correspondent local sublanguages as to \emph{co-faulty} and
\emph{co-non-faulty} ones. A formal definition of these sublanguages is
presented below, and then an algorithm which computes the co-faulty
and co-non-faulty sublanguages for all the system's modules, is given. 
% It is
% followed by algorithms which verify diagnosability and find a virtual module.

\subsection{Co-faulty and co-non-faulty sublanguages}

\begin{definition}
\label{def:co-faulty}
Given $i, j \in I$, $L_{i,f} \subseteq L_i$,
we say that a sublanguage $L_{j,cf} \subseteq L_j$ is \emph{co-faulty} with
respect to $L_{i,f}$ if 
$$
	(\forall s \in L_{j,cf})(\forall t \in P_i[P_j^{-1}(s)])
	\left[
		t \in L_{i,f} \land t \not \in L_{i,nf}   
	\right],
$$ 
and a sublanguage $L_{j,cnf} \subseteq L_j$ is
\emph{co-non-faulty} with respect to $L_{i,nf}$ if 
$$
	(\forall s \in L_{j,cnf})(\forall t \in P_i[P_j^{-1}(s)])
	\left[
		t \not \in L_{i,f} \land t \in L_{i,nf}   
	\right].
$$ 
\end{definition}

In words, the co-faulty sublanguage is a sublanguage which satisfies two
conditions:
a) it is the sublanguage of projection of the global faulty language
to the local language; b) the sublanguage is not co-non-faulty.
Similarly, the co-non-faulty sublanguage is a sublanguage which satisfies
conditions:
a) it is the sublanguage of projection of the global non-faulty language
to the local language; b) the sublanguage is not co-faulty.

% \begin{lemma}
% \label{lem:empty_co_if_no_common}  
% Given a language $L_j\mid j \in I$, its co-faulty and
% co-non-faulty sublanguages are empty, if the language has no common events in
% its strings, i.e
% $$P_{\Sigma_j \rightarrow \bigcap_{i\neq j}^I \Sigma_i}(L_i) = \emptyset.$$
% \end{lemma}
% We skip the proof due to its triviality. 

Given global faulty and non-faulty sublanguages, one can compute the local
co-faulty sublanguage, using the global language, as follows:
\begin{equation}
\label{eq:co-faulty_from_global}
	\begin{array}{l}
		L_{j,cf} := P_j(L_f) \backslash P_j(L_{nf}),\\ 
		L_{j,cnf} := P_j(L_{nf}) \backslash P_j(L_{f}).	
	\end{array}
\end{equation}
However, we are interested to compute local sub languages without computing the
global language. Since the global faulty sublanguage is define as
\begin{equation}
\label{eq:co-faulty_from_locals}
	L_f := P_i^{-1}(L_{i,f}) \cap \bigcap_{k\neq
	i}^I P_k^{-1}(L_k),
\end{equation}
then, by substituting the global language in \ref{eq:co-faulty_from_global} by
\ref{eq:co-faulty_from_locals}, and by mathematical induction, the co-faulty
sublanguage of an arbitrary module can be computed as follows:

\begin{equation}
\label{eq:co-faulty_iterative_w_faulty}
	\begin{array}{l}
		L_{j,cf} := 
		\\
		P_j\Big(P_j^{-1}(L_j) \cap P_i^{-1}(L_{i,f})\cap 
		\bigcap_k^I P_k^{-1}(L_{k,cf})\Big) \backslash 
		\\
		P_j\Big(P_j^{-1}(L_j) \cap P_i^{-1}(L_{i,nf})\cap 
		\bigcap_k^I P_k^{-1}(L_{k,cnf})\Big),
		\\ 
		\textrm{where } i\neq j\neq k \in I.
	\end{array}
\end{equation}

We skip the definition of co-non-faulty sublanguage here due to its similarity. 

\begin{alg}
\caption{Computing all co-faulty and co-non-faulty languages of
all the modules}
\begin{algorithmic}[1]
	\Require The set of the system's languages $\{L_j\mid j \in I\}$, faulty and
	non-faulty sublanguages $L_{i,f}$, $L_{i,nf}$ of a faulty module $i\in I$.
	\ForAll{$j \in I$}
	\label{alg:fcf_init}
		\Comment{Initialization}
		\State $\Sigma_{j,c} \leftarrow \Sigma_j \cap \bigcup_{i\neq j}^I\Sigma_i$
		\State $C_j \leftarrow P_{j,c}(L_j)$
		\State $F_j \leftarrow \emptyset, N_j \leftarrow \emptyset$
	\EndFor
	\Procedure{propagate-fn}{$k$, $F_k$, $N_k$}
		\ForAll{$j \in I \mid j\neq i, \Sigma_j \cap \Sigma_k \neq \emptyset,
				\Sigma_{j,c}\neq \emptyset$} 
			\State $F'_j \leftarrow P_{j,c}(F_k \parallel C_j)$
			\label{alg:fcf_partial_begin}
			\State $N'_j \leftarrow P_{j,c}(N_k \parallel C_j)$ 
			\State $K \leftarrow \overline{F'_j \cap N'_j}$
			\State $F'_j \leftarrow F'_j \backslash K$
			\State $N'_j \leftarrow N'_j \backslash K$
			\label{alg:fcf_partial_end}
			\If{$F'_j \backslash F_j \neq \emptyset \lor 
				 N'_j \backslash N_j \neq \emptyset$}
				\label{alg:fcf_update}
				\State $F_j \leftarrow F_j \cup F'_j$
				\State $N_j \leftarrow N_j \cup N'_j$
				\State $\Sigma_{j,c} \leftarrow
					\{\sigma \in s \}$, where
				\State $s \in
						\left[(\overline{F_j} \backslash F_j) \cup
						(\overline{N_j} \backslash N_j)\right] \backslash	
						(\overline{F_j} \cap \overline{N_j})
						$
				\State \textproc{propagate-fn}$(j, F_j, N_j)$
			\EndIf
		\EndFor
	\EndProcedure
	
	\State $F_i \leftarrow P_{i,c}(L_{i,f})$
		\label{alg:fcf_Fi}
	\State $N_i \leftarrow P_{i,c}(L_{i,nf})$
	\State \textproc{co-languages}($i$, $F_i$, $N_i$)
	\Comment{Beginning of recursion}	
	\ForAll{$j \in I \mid j \neq i$}
		\Comment{Finalization}
		\label{alg:fcf_final}
		\State $L_{j,cf} \leftarrow L_j \cap P_{j,c}^{-1}(F_j)$
		\State $L_{j,cnf} \leftarrow L_j \cap P_{j,c}^{-1}(N_j)$
	\EndFor
	\\
	\Return $\{L_{j,cf}\}$, $\{L_{j,cnf}\}$
\end{algorithmic}
\label{alg:propagate_fn}
\end{alg}

Now, we present Algorithm \ref{alg:propagate_fn} which, given a module with a
faulty behaviour defined, computes the co-faulty and co-non-faulty languages for
all the rest modules of the system.
The algorithm starts from a preliminary step at line \ref{alg:fcf_init}.
At this step a projection to the common events $C_j$ is computed for all the
local languages. Projections of co-faulty and co-non-faulty sublanguages to the
common events, denoted as $F_j, N_j$, are empty in the beginning. Event sets
$\Sigma_{j,c}$ are sets of the common events, which don't belong neither to
co-faulty and co-non-faulty sublanguages nor to intersection of the
sublanguages' prefix-closures. Since that sublanguages are not defined in the
beginning, the event sets contain all events from the projections. A role of
these sets will be clarified later.
The recursive procedure \emph{propagate-fn} computes $F_j$ and $N_j$ for all the
system's modules, except the module with a fault; the procedure operates with
common events only. Before entering the procedure the projections of the faulty
module's sublanguages, $F_i, N_i$ are computed at the step \ref{alg:fcf_Fi}.
Note, that projection operation preserves faulty and non-faulty information,
when faulty behaviour is defined in a specification-based way.

The recursive procedure computes all projections $F_j, N_j$ of the modules
adjacent to a given module $k$ (we say that two modules are adjacent to each
other if their languages have events in common). At the first steps
\ref{alg:fcf_partial_begin}-\ref{alg:fcf_partial_end} of the procedure we
compute $F'_j, N'_j$ with respect to the module $k$; these projections are
partial. The parallel composition $F_k \parallel C_j$, followed by projection to
the common events, is used to extract the faulty) information from the
language $F_k$ to $C_j$, and non-faulty from $N_k$ to $C_j$. At the step
\ref{alg:fcf_update} we check if some co-faulty or co-non-faulty strings should be added to the projections computed earlier. If so, then we update $F_j, N_j$, $\Sigma_{j,c}$ and call the same procedure to update projections of the adjacent modules. Thus, whenever the co-faulty or
co-non-faulty projections of that module changed, the projections $F_j, N_j$ are
updating with respect to every other module, due to recursion. The event sets
$\Sigma_{j,c}$ represent a potentiality that the projections $F_j, N_j$ can be
changed; the modules which have these sets empty can't change their language's
property with respect to the fault and, thus, are skipped during recursive
procedure. Finally, all the co-faulty and co-non-faulty sublanguages are
calculated for each module at the step \ref{alg:fcf_final}.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Construction of  virtual module}

\begin{alg} 
\caption{Computing observable information for the faulty module} 
\begin{algorithmic}[1]
	\Require The index  $i \in I$ of the faulty module, the index of a module with
	observable support $k \in I \mid M(L_{k,cf}) \neq \emptyset \lor M(L_{k,cnf})
	\neq \emptyset, k \neq i$, the sets $\{L_{j,cf}\}, \{L_{j,cnf}\}, j \in I$.
% 	\State $V \leftarrow \{i\}$ \Comment{Virtual module}

	\ForAll{$j \in I$}
	\label{alg:fco_init}
		\State $D_{j,f} \leftarrow P_{j,co}(L_{j,f})$
		\State $D_{j,nf} \leftarrow P_{j,co}(L_{j,nf})$
	\EndFor
	
	\Procedure{propagate-d}{$k$, $D_{k,f}$, $D_{k,nf}$}
		\ForAll{$j \in I \mid \Sigma_j \cap \Sigma_k \neq \emptyset$}
			\State $D'_{j,f} \leftarrow 
			P_{j,co}(F_j \parallel D_{k,f})$
			\If{$(D'_{j,f}\backslash D_{j,f} \neq \emptyset) \lor
				(D'_{j,nf}\backslash D_{j,nf} \neq \emptyset)$}
				\State $D_{j,f}\leftarrow D'_{j,f}$
				\State $D_{j,nf}\leftarrow D'_{j,nf}$
				\State \textproc{propagate-d}($j$, $D_{j,f}$, $D_{j,nf}$)
			\EndIf
		\EndFor 
	\EndProcedure
	
	\State \textproc{propagate-d}($k$, $D_{k,f}$, $D_{k,nf}$)
	\label{alg:fco_enter_recursion}
	\State $L_{i,f}^{ext} \leftarrow P_{i,co}(L_{i,f} \parallel D_{i,f})$
	\label{alg:fco_finalize}
	\State $L_{i,nf}^{ext} \leftarrow P_{i,co}(L_{i,nf} \parallel D_{i,nf})$
	\\
	\Return $L_{i,f}^{ext}, L_{i,nf}^{ext}$
\end{algorithmic}
\label{alg:propagate-d}
\end{alg}

The structure of the Algorithm \ref{alg:propagate-d} is similar to one
in Algorithm \ref{alg:propagate_fn}. It starts from computing projections to
common and observable events for the co-faulty and co-non-faulty sublanguages of each
module's language. Then, starting from the module $k$ which has observable
events in its sublanguages (i.e. it has potential observable support for a
sublanguage of the faulty module), begins a recursive procedure at step
\ref{alg:fco_enter_recursion}.
In the procedure we collect only observable events of other modules which are related to co-faulty or co-non-faulty
sublanguages. Then we propagated these events down to the faulty module.
Finally, at the step \ref{alg:fco_finalize}, the faulty and non-faulty
sublanguages of the faulty module are extended with observable events.

The result of the Algorithm \ref{alg:propagate-d}, the faulty and non-faulty
sublanguages extended with observable events, can be used to verify
diagnosability now. Any approach, which allows us to check for the presence of
indistinguishable strings in the language (the faulty and non-faulty
sublanguages can be united, if necessary), is suitable. We can have the
following outcomes after verification: a) no indistinguishable strings are
broken, b) no indistinguishable strings left, and c) some indistinguishable
strings are broken. In case (a) we pick another module $k \in I$ satisfying
requirements of the Algorithm \ref{alg:propagate-d} for further processing and
verification. In case (b) we may construct a virtual module of the faulty module
$i$ and the module $k$ and declare that the fault is diagnosable with respect to
the virtual module $\{i, k\}$ and stop, or continue and check if exists another
module which can also be used to build a virtual module. In case (c) we should
pick additional module satisfying requirements of the Algorithm
\ref{alg:propagate-d} and continue the process until all the indistinguishable
strings are broken. The following section analyzes what may be considered as a
criteria for choosing the module with observable support $k$.


\subsection{Algorithm to choose a module with observable support}
Assume that the objective function is to have the number of modules in the
system as many as possible, i.e. to have the maximal cardinality of the
partition $J$.
Given an initial set of languages, let rank of $J$ be equal to 0, i.e. $|J| =
|I|$. Let $F$ denotes the subset of languages with faults, and $M$ denotes the
subset of languages with correspondent observable supports.
Assume that it is always possible to make the system modularly diagnosable with
respect to some virtual modules. Then we know that $(\forall f \in F)~\exists m
\in M$. Let $F \cap M = \emptyset$ and $|M| \geq |F|$. Then, to make the system
modularly diagnosable it is required, in the worst case, $|F|$ members of $M$.
Thus, the cardinality of the systems with virtual modules, i.e. the cardinality
of the partition, in the worst case is:
\begin{equation}
	\min |J| = |I| - |F|.
\end{equation}
Let $M \subseteq F$. Then, the cardinality of the partition in the best case
is:
\begin{equation}
	\max |J| = |I| - \left(
		\left\lfloor \frac{|F|}{2} \right\rfloor + \textrm{mod} \frac{|F|}{2}
		\right). 
\end{equation}

As can be seen from the above, in order to maximize the number of modules while
making the virtual modules, we should consider, firstly, the modules which
themselves have faults. We propose a procedure for the given objective function
as follows:

Given the system of cardinality $|I|$, the subset $F \subseteq I$ of modules
with faults, such that any $f\in F$ is not diagnosable locally, the subset $M
\subseteq I$ of modules with observable supports, such that $(\forall f \in
F)~\{m \in M\}\neq \emptyset$. In order to make the system diagnosable by
the minimal number of virtual modules:
\begin{enumerate}
  \item Initially set the partition $J$ of $I$ such that the rank of $J$ is
  equal to 0;
  \item $(\forall j \in J, f \in j)$ update $j$ as follows: 
  	$j := j \cup \{m \in M \cap F\}$ if $M \cap F \neq \emptyset$,
 $j := j \cup \{m \in M\}$ otherwise, where $\{m\}$ is a singleton of the
 arbitrary chosen observable support for the given $f$, such that the new $j$
 is locally diagnosable; exclude $m$ from $k \in J \mid k \neq j$, and remove
 $k$ from $J$ if $k=\emptyset$.
\end{enumerate} 
The order the observable supports are verified in the procedure guaranties that
we consider the languages which themselves contain the faulty
sublanguages at first, thus maximizing the number of virtual modules in the
system.

It worth to note that the above algorithm can be augmented by additional
criteria aimed, for instance, to decrease computational burden.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Example}
\label{sec:Example}
An example with languages presented by automata (see the Figures \ref{fig:G1-4}
-- \ref{fig:L1_extended}) shows how the algorithms \ref{alg:propagate_fn} and
\ref{alg:propagate-d} can be applied to a simple system. We use marked states to
mark strings in languages, since they are not prefix-closed, in general. The
system consists of three modules as depicted in Figure \ref{fig:G1-4}. Here a
fault is presented only in the language $L_1$ by the event $f$.
Figure \ref{fig:G1_faulty} depicts faulty and non-faulty sublanguages of the
language $L_1$. Projections of these sublanguages to the common events (step
\ref{alg:fcf_Fi} of the Algorithm \ref{alg:propagate_fn}), $F_1$ and $N_1$ are
depicted in the Figure \ref{fig:FN}. Suppose that in the beginning of the
recursive procedure we pick module $2$. The figure depicts the co-faulty
and co-non-faulty sublanguage of the language $L_2$ with respect to the language
$L_1$, calculated at the steps \ref{alg:fcf_partial_begin} of the algorithm (we
don't show intermediate automata, reflecting compositional steps, due to space
restrictions). Note, that, when calculated, the event set $\Sigma_{2,c}$ is
empty for module $2$. Hence this module will not participate in the procedure
as a module adjacent to others. At the next step we randomly pick the language
$L_4$, and compute $F_4$ and $N_4$ with respect to the module $2$. Now, note
that $\Sigma_{3,c}:= \{e\}$, since this event is neither in the co-faulty and
co-non-faulty projections nor in their common prefix. The iterations is followed
by the module $3$, which has module $4$ as an adjacent one. Therefore, the
sublanguages of this module are updated.

Figure \ref{fig:L4_f} depicts co-faulty and co-non-faulty sublanguages of module
$4$ calculated at the step \ref{alg:fco_finalize} of the Algorithm
\ref{alg:propagate_fn}. It shows that the co-faulty sublanguage of the module
has an observable support; it satisfies the requirements of the Lemma
\ref{lem:distinguished}. Other modules with no faults have no observable
events; they have no observable supports, and not depicted.

The major steps of Algorithm \ref{alg:propagate-d} are depicted in the Figure
\ref{fig:D}. It is shown how the observable information from the module $4$ is
propagated backward to the language of the module $1$. The final step of the
algorithm is depicted in the Figure \ref{fig:L1_extended}. Clearly, the faulty
and non-faulty sublanguages, extended with observable information, have
distinguished observations. Then, we can conclude that the virtual module
composed of the modules $1$ and $4$ is locally diagnosable. Hence, the system is
modularly diagnosable with modularity presented by the partition 
$\{\{1,4\}, \{2\}, \{3\}\}$.



\begin{figure}[t]
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
% G1
\node[initial,state] (0)                    {$0$};
\node[above left = 0.5em of 0]{$L_{1}$};
\node[state, accepting]         (1) [above right of=0] {$1$};
\node[state, accepting]         (2) [right of=1]       {$2$};
\node[state, accepting]         (3) [right of=2]       {$3$};
\node[state, accepting]         (4) [right of=3]       {$4$};
\node[state, accepting]         (5) [right of=0] 		{$5$};
\node[]         () [below right of=0] 		{}; %some blank space
\path
(0)	edge [] 		 node {$f$} (1)
(1)	edge [] 		 node {$a$} (2)
(2)	edge [] 		 node {$o_1$} (3)
(3)	edge [] 		 node {$b$} (4)
(4)	edge [loop right] node {$c$} (4)
(0)	edge [] 		 node {$o_1$} (5)
(5)	edge [loop right] node {$c$} (5)
;
\end{tikzpicture}
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
% G2
\node[initial,state, accepting] (0)                    {$0$};
\node[above left = 0.5em of 0]{$L_{2}$};
\node[state, accepting]         (1) [right of=0] 		{$1$};
\node[state, accepting]         (2) [right of=1]       {$2$};
\path
(0)	edge [] 		  node {$a$} (1)
	edge [loop below] node {$c$} (0)
(1)	edge [] 		  node {$d$} (2)
(2)	edge [loop right] node {$c$} (2)
;
% G3
\node[initial,state, accepting] (0') [below of=0]      {$0$};
\node[above left = 0.5em of 0']{$L_{3}$};
\node[state, accepting]         (1') [right of=0']		{$1$};
\node[state, accepting]         (2') [right of=1']     {$2$};
\path
(0')	edge [] 		  node {$b$} (1')
		edge [loop below] node {$c$} (0')
(1')	edge [] 		  node {$e$} (2')
(2')	edge [loop right] node {$c$} (2')
;
% G4
\node[initial,state, accepting] (0'') [below of=0']  {$0$};
\node[above left = 0.5em of 0'']{$L_{4}$}; 
\node[state, accepting]         (1'') [right of=0'']	{$1$};
\node[state, accepting]         (2'') [right of=1'']   {$2$};
\node[state, accepting]         (3'') [right of=2'']   {$3$};
\path
(0'')	edge [] 		  node {$e$} (1'')
		edge [loop below] node {$c$} (0'')
(1'')	edge [] 		  node {$o_2$} (2'')
(2'')	edge [] 		  node {$d$} (3'')
(3'')	edge [loop right] node {$c$} (3'')
;
\end{tikzpicture}
\caption{Automata marking languages $L_1, L_2, L_3$ and $L_4$. $\Sigma_o :=
\{o_1, o_2\}$, $\Sigma_f := \{f\}$}
\label{fig:G1-4}
\end{figure}

% Fautly and non-faulty
\begin{figure}[t]
% \centering
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
\node[initial,state] (0)                    {$0$};
% \node[above = 3em of 0] {}; %adds some space above
\node[above left = 0.5em of 0]{$L_{1,f}$};
\node[state, accepting, fill=orange]         (1) [right of=0] 		{$1$};
\node[state, accepting, fill=orange]         (2) [right of=1]       {$2$};
\node[state, accepting, fill=orange]         (3) [right of=2]       {$3$};
\node[state, accepting, fill=orange]         (4) [right of=3]       {$4$};

\node[initial,state] (0') [below of=0]                   {$0$};
\node[above left = 0.5em of 0']{$L_{1,nf}$};
\node[state, accepting]         (5)
[right of=0'] 		{$5$};

\path
(0)	edge [] 		 node {$f$} (1)
(1)	edge [] 		 node {$a$} (2)
(2)	edge [] 		 node {$o_1$} (3)
(3)	edge [] 		 node {$b$} (4)
(4)	edge [loop below] node {$c$} (4)
;
\path
(0') edge [] 		 node {$o_1$} (5)
(5)	edge [loop right] node {$c$} (5)
;
\end{tikzpicture}
\caption{Automata marking the faulty and non-faulty sublanguages of $L_1$}
\label{fig:G1_faulty}
% \end{figure}

% Projection to common events (G1)
% \begin{figure}[t!]
% \centering
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
\node[initial,state] (0)                    {$0$};
% \node[above = 3em of 0] {}; %adds some space above
\node[above left = 0.5em of 0]{$F_1$};
\node[state, accepting, fill=orange]         (2) [right of=0]       {$2$};
\node[state, accepting, fill=orange]         (4) [right of=2]       {$4$};

\node[initial,state] (0') [] at (5,0)              {$0$};
\node[above left = 0.5em of 0']{$N_1$};
\node[state, accepting]         (5) [right of=0'] 		{$5$};

\path
(0)	edge [] 		 node {$a$} (2)
(2)	edge [] 		 node {$b$} (4)
(4)	edge [loop right] node {$c$} (4)
;
\path
(0') edge [] 		 node {$c$} (5)
(5)	edge [loop right] node {$c$} (5)
;
\end{tikzpicture}
\\

\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
% F2
\node[initial,state] (0)                    {$0$};
\node[above left = 0.5em of 0]{$F_2$};
\node[state, accepting, fill=orange]         (1) [right of=0] 		{$1$};
\node[state, accepting, fill=orange]         (2) [right of=1]       {$2$};
\path
(0)	edge [] 		  node {$a$} (1)
(1)	edge [] 		  node {$d$} (2)
(2)	edge [loop right] node {$c$} (2)
;
% F2
\node[initial,state, accepting] (0') at (5,0) {$0$};
\node[above left = 0.5em of 0']{$N_2$};
\path
(0') edge [loop below] node {$c$} (0')
;
\end{tikzpicture}
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
% F4
\node[initial,state] (0)                    {$0$};
\node[above left = 0.5em of 0]{$F_4$};
\node[state ]         (1) [right of=0] 		{$1$};
\node[state, accepting, fill=orange]         (2) [right of=1]       {$2$};
\path
(0)	edge [] 		  node {$e$} (1)
(1)	edge [] 		  node {$d$} (2)
(2)	edge [loop right] node {$c$} (2)
;
\node[initial,state, accepting] (0') at (5,0) {$0$};
\node[above left = 0.5em of 0']{$N_4$};
\path
(0') edge [loop below] node {$c$} (0')
;
\end{tikzpicture}
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5}, 
	every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
% F3
\node[initial,state] (0)                    {$0$};
\node[above left = 0.5em of 0]{$F_3$};
\node[state, accepting, fill=orange]         (1) [right of=0] 		{$1$};
\node[state, accepting, fill=orange]         (2) [right of=1]       {$2$};
\path
(0)	edge [] 		  node {$b$} (1)
(1)	edge [] 		  node {$e$} (2)
(2)	edge [loop right] node {$c$} (2)
;
\node[initial,state, accepting] (0') at (5,0) {$0$};
\node[above left = 0.5em of 0']{$N_3$};
\path
(0') edge [loop below] node {$c$} (0')
;
\end{tikzpicture}
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
% F4
\node[initial,state] (0)                    {$0$};
\node[above left = 0.5em of 0]{$F_4$};
\node[state, accepting, fill=orange]         (1) [right of=0] 		{$1$};
\node[state, accepting, fill=orange]         (2) [right of=1]       {$2$};
\path
(0)	edge [] 		  node {$e$} (1)
(1)	edge [] 		  node {$d$} (2)
(2)	edge [loop right] node {$c$} (2)
;
\node[initial,state, accepting] (0') at (5,0) {$0$};
\node[above left = 0.5em of 0']{$N_4$};
\path
(0') edge [loop below] node {$c$} (0')
;
\end{tikzpicture}

\caption{Automata marking sublanguages $F_1$ and $N_1$ of the faulty module,
and co-faulty and co-non-faulty languages of the modules 2, 3 and 4 in the
order they are composed (top-down): 1-2, 2-4, 1-3, 3-4. Note, that the
sublanguage $F_4$ is defined partially at first, then fully}
\label{fig:FN}
\end{figure}

% Fautly and non-faulty
\begin{figure}[t]
% \centering
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
\node[initial,state] (0) {$0$};
\node[above = 0.5em of 0]{$L_{4,cf}$}; 
\node[state, accepting, fill=orange]         (1) [right of=0]	{$1$};
\node[state, accepting, fill=orange]         (2) [right of=1]   {$2$};
\node[state, accepting, fill=orange]         (3) [right of=2]   {$3$};
\path
(0)	edge [] 		  node {$e$} (1)
(1)	edge [] 		  node {$o_2$} (2)
(2)	edge [] 		  node {$d$} (3)
(3)	edge [loop right] node {$c$} (3)
;
\node[initial,state, accepting] (0') [below of=0] {$0$};
\node[above left = 0.5em of 0']{$L_{4,cnf}$};
\path
(0') edge [loop below] node {$c$} (0')
;
\end{tikzpicture}
\caption{Automata marking co-faulty and co-non-faulty sublanguages of
the language $L_4$. Automata for the sublanguages of the modules 2 and 3 are
equal to the ones depicted in the Figure \ref{fig:FN}}
\label{fig:L4_f}
% \end{figure}

% Projections to common and observable events
% \begin{figure}[t]
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5}, 
	every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
% F3
\node[initial,state] (0)                    {$0$};
% \node[above = 3em of 0] {}; %adds some space above
\node[above left = 0.5em of 0]{$D_{3,f}$};
\node[state, accepting, fill=orange]         (1) [right of=0] 		{$1$};
\node[state, accepting, fill=orange]         (2) [right of=1]       {$2$};
\node[state, accepting, fill=orange]         (2') [right of=2]       {$2'$};
\path
(0)	edge [] 		  node {$b$} (1)
(1)	edge [] 		  node {$e$} (2)
(2)	edge [] 		  node {$o_2$} (2')
(2')	edge [loop right] node {$c$} (2')
;
\end{tikzpicture}
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
\node[initial,state] (0)                    {$0$};
\node[above left = 0.5em of 0]{$D_{2,f}$};
\node[state, accepting, fill=orange]         (1) [right of=0] 		{$1$};
\node[state, accepting, fill=orange]         (1') [right of=1] 		{$1'$};
\node[state, accepting, fill=orange]         (2) [right of=1']       {$2$};
\path
(0)	edge [] 		  node {$a$} (1)
(1)	edge [] 		  node {$o_2$} (1')
(1')edge [] 		  node {$d$} (2)
(2)	edge [loop right] node {$c$} (2)
;
\end{tikzpicture}
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
\node[initial,state] (0)                    {$0$};
\node[above left = 0.5em of 0]{$D_{1,f}$};
\node[state, accepting, fill=orange]         (2) [right of=0]       {$2$};
\node[state, accepting, fill=orange]         (2') [below of=2]      
{$2'$}; \node[state, accepting, fill=orange]         (4) [right of=2]      {$4$};
\node[state, accepting, fill=orange]         (4')[below of=4]{$4'$};
\path
(0)	edge [] 		 node {$a$} (2)
(2)	edge [] 		 node {$b$} (4)
	edge [] 		node {$o_2$} (2')
(2')edge [] 		 node {$b$} (4')
(4)	edge [loop right] node {$c$} (4)
	edge [] 		node {$o_2$} (4')
(4')edge [loop right] node {$c$} (4')
;
\end{tikzpicture}
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
\node[initial,state] (0)                    {$0$};
\node[above left = 0.5em of 0]{$D_{1,f}$};
\node[state, accepting, fill=orange]         (2) [right of=0]       {$2$};
\node[state, accepting, fill=orange]         (4) [right of=2]       {$4$};
\node[state, accepting, fill=orange]         (4')[right of=4] {$4'$};
\path
(0)	edge [] 		 node {$a$} (2)
(2)	edge [] 		 node {$b$} (4)
(4) edge [] 		node {$o_2$} (4')
(4')edge [loop right] node {$c$} (4')
;
\end{tikzpicture}
\caption{Automata marking $D_{j,f}$ of the modules 1, 2 and 3 in
the order they are composed (top-down): 4-3, 4-2, 2-1, 3-1. Automata marking
$D_{j,nf}$ are not depicted since they have no observable events}
\label{fig:D}
% \end{figure}


% Fautly and non-faulty
% \begin{figure}[t!]
% \centering
\begin{tikzpicture}[->,>=stealth, node distance=2cm, auto, shorten >=1pt,
semithick, initial text=,	
	every node/.style={scale=0.5},
    every state/.style={fill=green!40,text=black},
    accepting/.style={double distance=1.5pt, outer sep=0.75pt+\pgflinewidth}
    ]
% \draw[help lines] (0,-2) grid (6,2);
\node[initial,state] (0)                    {$0$};
% \node[above = 3em of 0] {}; %adds some space above
\node[above left = 0.5em of 0]{$L_{1,f}$};
\node[state, accepting, fill=orange]         (1) [right of=0] 		{$1$};
\node[state, accepting, fill=orange]         (2) [right of=1]       {$2$};
\node[state, accepting, fill=orange]         (3) [right of=2]       {$3$};
\node[state, accepting, fill=orange]         (4) [right of=3]       {$4$};
\node[state, accepting, fill=orange]         (4')[right of=4]       {$4'$};

\node[initial,state] (0') [below of=0]                   {$0$};
\node[above left = 0.5em of 0']{$L_{1,nf}$};
\node[state, accepting]         (5)
[right of=0'] 		{$5$};

\path
(0)	edge [] 		 node {$f$} (1)
(1)	edge [] 		 node {$a$} (2)
(2)	edge [] 		 node {$o_1$} (3)
(3)	edge [] 		 node {$b$} (4)
(4) edge [] 		 node {$o_2$} (4')
(4')edge [loop below] node {$c$} (4')

;
\path
(0') edge [] 		 node {$o_1$} (5)
(5)	edge [loop right] node {$c$} (5)
;
\end{tikzpicture}
\caption{Automata marking the faulty and non-faulty sublanguages of $L_1$ after
the backward Algorithm. The observation of $L_{1,f}$ is $\{o_1o_2\}$ differs
from the observation of $L_{1,nf}$ which is $\{o_1\}$}
\label{fig:L1_extended}
\end{figure}


\section{Modular Virtual Diagnosability}